When are Fuzzy Extractors Possible?

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
changing notation from balls/bins

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 1-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \thref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.  its the same corollary}

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Insufficiency of $\Hfuzz(W)$ to secure sketch from distribution families}
\label{sec:family of dist}

In the previous section, we showed the sufficiency of $\Hfuzz$ for known distribution algorithms.  Unfortunately, it is unrealistic to assume that $W$ is completely known.  Traditionally, algorithms deal with this uncertainty by providing security for a family of distributions $\mathcal{W}$.

In this section, we show uncertainty of $W$ comes at a real cost. 
We will show a family $\mathcal{W}$~(where each member has fuzzy min-entropy) where any secure sketch for $\mathcal{W}$ leaves almost no entropy.  A key aspect is formalizing the difference between the views of the fuzzy extractor~(which knows the family $\mathcal{W}$ and the sample $w$) and the view of the adversary~(knows the particular distribution $W$ but not the sample $w$).

\subsection{A definitional equivalence}
\label{sec:def equiv}
%We refer to $\mathcal{W}$ as the \emph{family}, the distribution $W$ as a \emph{source} and the particular outcome taken $w\in W$ as the \emph{sample}.

The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{W}$.  The challenger wins if the adversary cannot guess the outcome of $W$ with high probability, and the adversary wins otherwise.  Let $V$ is a distribution over elements of $\mathcal{W}$.  The minimax theorem says we can reverse which of these actions is announced first~\cite{neumann1928theorie} if $\mathcal{A}$ announces a distribution $V$ instead of a single element $W$.  That is, the following two player games have the same equilibrium:

%More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively. We provide two formulations of a two player game.\footnote{We denote the outcome of the game as a reward to each player.  This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.  This is to apply results from game theory.}

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}}_1(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{W})$\\
$W \leftarrow \mathcal{A}(\mathcal{W}, \sketch, \rec)$\\
If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing} 
\vspace{.065in}
\end{minipage}  &
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{W}}_2(\mathcal{A}, \mathcal{C}, \tilde{m})$: \\
$V \leftarrow \mathcal{A}(\mathcal{W})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(V, \mathcal{W})$\\
$W \leftarrow V$\\
If $W\not\in \mathcal{W}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge \tilde{m}$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing}
\end{minipage}
\end{tabular}
\end{center}

%The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{W}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.  In $\Exp^{\mathcal{W}}_2$, the adversary specifies a distribution $V$ over sources, and the challenger then specifies their algorithm.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{W}$ be a family of distributions.  If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.  Let $V$ be a distribution over $\mathcal{W}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

In our negative results, the adversary that specifies a distribution $V$ over $\mathcal{W}$.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  An alternate view is that $(\sketch, \rec)$ sees a distribution $V$ while the adversary sees side information $Z$~(corresponding to the distribution $W$).

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{W}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{W}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch.
\end{corollary}

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.

\subsection{Insufficiency of $\Hfuzz(W)$ to secure sketch from families of distributions}
We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} \ge 1$ for $t\ge 4$.  
\end{theorem}

\begin{proof}
We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}$ be the set of all distributions of the form 
\[W =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} W_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i, b_i\in\mathbb{F}, a_i\neq 0$.  
This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over $\mathcal{W}$.  The adversary sees $\sketch(V)$ and $Z$.  $Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. The algorithms $\sketch, \rec$ never see $Z$.
Fix some $4\le t < \gamma$.
We show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 1$.
\item By \corref{cor:no fuzz for dist}, since no secure sketch can support the uniform distribution $V$ over $\mathcal{W}$, there is no secure sketch for the family $\mathcal{W}$.\end{itemize}
\end{proof}
\bnote{should note we can decrease field size at the cost of distance.}
\subsubsection{Implications for Computational secure sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ parameters to the definition, representing the distinguishing circuit).  By the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:

\begin{corollary}
\label{cor:imposs comp sketch}
Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.  There exists a family of distributions $\mathcal{W}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.  If 
$s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
$t\ge 4$, and 
 $\epsilon_{sec} + t\delta < 1/16$,
 then $\tilde{m} =O(1)$.
\end{corollary}

@@

\section{Insufficiency of $\Hfuzz(W)$ to fuzzy extract from distribution families}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$, for $\kappa \ge 1$ such that $\epsilon \le 1/4 - \ngl(n)$ for $t = \omega(n^{1/2}\log n)$. \end{theorem}

\begin{proof}[Proof Outline]
Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  In particular, we need to assume a larger error tolerance.  Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.

We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.
Define the distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.  Let $V$ be the uniform distribution over elements $\mathcal{W}$ and $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.
We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: for many values of $Z$ and for half of the $\key \in\zo^\kappa$, there are no viable $v\in\mathcal{M}$.  In more detail,
\begin{itemize}
\item Half the keys have at most $2^{n- (\kappa-1)}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
\item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.  All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).  We show that most of $V_\key$ is near a boundary.  A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short} .  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  Together these two results imply that $V_\key$ is small.
\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ is empty.  Thus, for most values of $Z$, any key lying in $R_{small}$ can be labeled as ``random''.
\end{itemize}
\item By \corref{cor:no fuzz for dist}, since no fuzzy extractor can support the uniform distribution over $\mathcal{W}$, there is no fuzzy extractor for the family $\mathcal{W}$.
\end{itemize}

@@

\begin{lemma}
\label{lem:secure sketch entropy loss}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  We do not consider these coins in our security analysis~(and thus, they can be considered private).  \bnote{is this really okay?  I know its just another markov but it makes me nervous}
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
\[
\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

@@

\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <1$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  %Having seen $V$ there are many possible values for $Z$.  Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.  
 The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

@@

Many of these sets must be small.  That is, there exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa-1} = 2^{n-\kappa +1}$.  If not, there exists a set of $\key$ of size $2^{\kappa-1}$ that all have at least $\mathcal{M}/2^{\kappa-1}$ points.\footnote{In the case where $\kappa=1$, $R_{small}$ still has at least one element.}  This is more points than exist in the metric space.

>>>>

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W)=\Hoo(W)$, because all points in $W$ are distance at least $t$ apart. Our proof relies on high dimensionality of $W$ and on perfect correctness of the $\rep$ procedure.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

We show comparable, but stronger, results for secure sketches.  Namely, we show in \corref{cons:leveling} that secure sketches are possible if the distribution $W$ is precisely known. (In fact, we obtain our fuzzy extractors for the case of a known distribution from this result by applying a randomness extractor.) \bnote{should be citing same thing for sketch and fuzzy extractor.  its the same corollary}

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of secure sketches for all families with $\Hfuzz$}
\label{sec:family of dist}

In the previous section, we showed the sufficiency of $\Hfuzz(W)$ for known distribution algorithms.  Unfortunately, it is unrealistic to assume that $W$ is completely known.  Traditionally, algorithms deal with this uncertainty by providing security for a family of distributions $\mathcal{W}$.

In this section, we show uncertainty of $W$ comes at a real cost.  The security game of a fuzzy extractor can be thought of as a three stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary sees $(\sketch, \rec)$ and specifies $W\in \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W))< \tilde{m}$.  
We prove impossibility in a game that is harder for the adversary to win: 1) the challenger specifies $(\sketch, \rec)$ 2) the adversary samples a random distribution from $W\leftarrow \mathcal{W}$ 3) the adversary wins if $\Hav(W|\sketch(W)) < \tilde{m}$.

Let $V$ be the process of uniformly sampling $W\leftarrow \mathcal{W}$ and then sampling $w\leftarrow W$.  Let $Z$ be the description of which $W$ was sampled.  The view of the challenger is $V$, while the view of the adversary is a distribution $V|Z$ where $Z$ is the description of which $W$ was sampled.  Our results rule out security for an average member of $\mathcal{W}$.  It may be possible to improve parameters by ruling out only a worst case $W$.  In \apref{sec:def equiv}, we show that providing security for a family $\mathcal{W}$ is equivalent to providing security for all distributions over that family.

We now show a family of distributions $\mathcal{W}$ that does not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$, for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta <1/4$ and $t\ge 4$ then $\tilde{m}<2$.

Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Then, 
\[
\Hav(V|\sketch(V), Z)< 2.
\]
\end{theorem}

\begin{proof}
We prove the stronger average case statement.
We first describe a family $\mathcal{W}$.  Let $\mathbb{F}$ be some field of size $q =\omega(\poly(n))$.  
Let $\mathcal{W}$ be the set of all distributions of the form 
\[W =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{\gamma} \end{pmatrix} W_1 + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{\gamma} \end{pmatrix} 
\]
where $W_1$ is uniform and $W_i = a_i W_1 + b_i$ for $2\le i \le \gamma$ and $a_i, b_i\in\mathbb{F}, a_i\neq 0$.  
This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.  The adversary sees $\sketch(V)$ and $Z$.  $Z$ is the description of the line $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. The algorithms $\sketch, \rec$ never see $Z$.
Fix some $4\le t < \gamma$.
We show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
\subsection{Implications for Computational secure sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

A \emph{HILL secure sketch} is obtained by replacing the security condition in \defref{def:secure sketch} with HILL entropy~(adding parameters $\epsilon_{sec}, s_{sec}$ to the definition, representing the distinguishing circuit).  By the contrapositive of~\cite[Corollary 3.8]{fuller2013computational}, no sketch can retain HILL entropy for the same family of distributions:

\begin{corollary}
\label{cor:imposs comp sketch}
Let $n$ be a security parameter and let $\mathcal{M} = |\mathbb{F}|^\gamma$.  There exists a family of distributions $\mathcal{W}$ over $\mathcal{M}$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$ and for any $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-HILL secure sketch $(\sketch, \rec)$ that is $(s_{sec}, \epsilon_{sec})$-hard and error $\delta$.  If 
$s_{sec}\ge t(|\rec| + \gamma \log |\mathbb{F}|)$, 
$t\ge 4$, and 
 $\epsilon_{sec} + t\delta < 1/16$,
 then $\tilde{m} <4$.
\end{corollary}

@@

\section{Impossibility of fuzzy extractors for all families with $\Hfuzz$}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.

\begin{theorem}
\label{thm:imposs fuzz ext}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{W}$ over $\zo^n$ such that for each element $W\in \mathcal{W}$, $\Hfuzz(W)= \omega(\log n)$.  Let $\kappa \ge 2$, $t = \omega(n^{1/2}\log n)$.  Any $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta = 0$ has $\epsilon > 1/8 - \ngl(n)$.

Furthermore, this is true on average.  Let $V$ be process of uniformly sampling $W\leftarrow \mathcal{W}$ and sampling $w\leftarrow W$ and let $Z$ be the description of which $W$ is sampled.  Let $(\Key, P)\leftarrow \gen(V)$.  Then, 
\[
\sd ((\Key,P, Z), (U_\kappa, P, Z))>1/8-\ngl(n).
\]

\end{theorem}

\begin{proof}[Proof Outline]
We prove the stronger average case statement.
Let $\nu = \omega(\log n)$ and $\nu = o(n^{1/2}/\log n)$.  Let $t=4\nu n^{1/2}$ and note that $n/\nu >t$.

Our counterexample uses a slightly different family of distributions $\mathcal{W}$ than the counterexample for secure sketches.  
We can't work directly on the Hamming distance over a large alphabet~(as we did for secure sketches).  We embed this larger space to the binary Hamming metric.
Let $x_1,..., x_\nu \in \zo^\nu$.  Let $\mathbb{F}$ denote the field of size $2^{\nu}$.  Let $a_2,..., a_{n/\nu}\in\mathbb{F}$ such that $a_i\neq 0$ and let $b_2,..., b_{n/\nu}\in\mathbb{F}$.  
Interpret $x_1,..., x_{\nu}$ as a element $x\in \mathbb{F}$ and let 
\[w =  \begin{pmatrix} \vec{1} \\a_2  \\ \vdots \\ a_{n/\nu} \end{pmatrix} x + \begin{pmatrix} 0  \\ 
b_2\\ \vdots \\ b_{n/\nu} \end{pmatrix} .
\]
The multiplication is in $\mathbb{F}$.
Define a distribution $W$ as the uniform distribution over values of $x$ for a particular value of $a_2,..., a_{n/\nu}$, $b_2,..., b_{n/\nu}$.  
Let $\mathcal{W}$ be the set of all such $W$.

 Define $V$ as the process of uniformly choosing $W\leftarrow \mathcal{W}$ and then sampling from $w\leftarrow W$.  The adversary sees $\sketch(V)$ and which distribution was sampled, call this information $Z$. $Z$ is the description of the line $Z = a_2,..., a_{n/\nu}, b_2, ..., b_{n/\nu}$.

We now present an outline of the proof~(proofs in \apref{sec:fuzz ext proof}):
\begin{itemize}
\item \propref{prop:dist fuzzy ent fuzz}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:dist uniform fuzz}: the distribution $V$ is uniform.
\item \lemref{lem:fuzz can't get key}: In expectation across $Z$, a large subset of keys that are not possible.  In more detail,
\begin{itemize}
\item Half the keys have at most $2^{n- \kappa}$ pre images in the metric space~(this is at most half the metric space).  Denote this set as $R_{small}$.  
\item Consider some $\key \in R_{small}$.  %Our goal is to show there are few values of $v \in V|Z$ that could produce this key.  
Consider the set of $V_{\key } = \{w | \rep(w, p) = \key \}$.  All points in $V | \sketch(V)$ are distance $t$ from a boundary of $V_\key$~(the functionality of $\rep$ guarantees that for the true $w$ all nearby points map to the same $\key$).  We show that most of $V_\key$ is near a boundary.  A result of Frankel and F{\"u}redi says that the boundary of a region is minimized by a ball containing the same number of points~\cite{frankl1981short}.  Hoeffding's inequality says that most of a ball lies near its boundary~\cite{hoeffding1963probability}.  Together these two results imply that $V_\key$ is small.
\item As before, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
\item For most values of possible $Z$, the intersection between the viable pre images of $V|Z$ and $V_\key$ contains at most one point~(the received point $v$).  Checking if $V|Z \cap V_{\key}$ is nonempty is an effective distinguisher.
%The previous two propositions were similar to the secure sketch counterexample.  However, the structure on the metric space imposed byThe remainder of the proof is significantly different.  We show for any $(\gen, \rep)$ many keys have few possible values that could produce them in the metric space once $p$ is published.  Then an adversary that sees $z$ is able to eliminate many possible keys and thus effectively distinguish the key from random.
\end{itemize}
\end{itemize}

@@

\begin{lemma}
\label{lem:secure sketch entropy loss}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\gamma-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  This is the same as considering $\rep$ that outputs any coin it flips.  Since $w, w'$ are independent of $p$ this does not effect correctness.  Security is defined based on the output of $\rec$ so outputting the coins of $\rep$ does not effect security.
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \Pr_{ss\leftarrow \sketch(w)} [\rec(w', ss) \neq w] < 1/4.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[ss\in A_{ss}]\ge 1/2$ and $\forall ss\in A_{ss}$, 
\[
\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

@@

\begin{lemma}
\label{lem:side info determines sketch}
$\Hav(V | \sketch(V), Z) <2$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\gamma$ coefficients and there are $(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}$ equally likely values for $Z$.
 As described above, the view of $\sketch, \rec$ is a uniform distribution $V$.  %Having seen $V$ there are many possible values for $Z$.  Furthermore, the distributions $V|Z$ have disjoint support outside of the observed point.  
 The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\gamma$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\gamma-1} |\mathbb{F}|^{\gamma-1}}{|\mathbb{F}|^\gamma}\right) = \log \left( (|\mathbb{F}|-1)^{\gamma-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$~(having seen $v$).  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

@@

There exists a set $R_{small}$  where $|R_{small} | \ge 2^{\kappa-1}$ such that for all $\key\in R_{small}$,  $|Q_{p^*, r}|\le \mathcal{M}/2^{\kappa} = 2^{n-\kappa }$.  If not, then $\cup_{\key} |Q_{p^*, \key}| > |\mathcal{M}|$.
For the remainder of the proof we restrict ourselves to elements in $R_{small}$.  Only points that are distance $t$ from points outside of $Q_{p^*, r}$ are viable points in the metric space.  These are the interior of $Q_{p^*, r}$:
\begin{align*}
\inter(Q_{p^*, \key}) = \{w | \rep(w, p^*) = \key \wedge \forall w', \dis(w, w') \le t \wedge \rep(w', p^*) =\key\},\\
%\crust(Q_{p^*, r}) = \{w | \rep(w, p^*) = r \wedge \exists w', \dis(w, w')\le t \wedge \rep(w', p^*) \neq r\}.
\end{align*}
